---
title: "ESSN_Chinook_2018_postseason"
author: "Andy Barclay"
date: "January 9, 2019"
output: html_document
---

##Set up workspace
###Get functions and load tidy packages
```{r workspace setup, echo=FALSE}

source("C:\\Users\\awbarclay\\Documents\\R\\GitHubCloneFunctions.R")#GCL functions
source("V:\\Analysis\\Staff\\Andy Barclay\\R\\New Functions\\WorkspaceFolders.GCL.R")#A function I wrote

library("tidyverse")

```

###Create output folders 
```{r create folders, echo=TRUE, message=FALSE}

#WorkspaceFolders.GCL(Folders=c("Output","bayes","objects","rubias"),Subfolders=list(bayes=c("baseline","mixture","control","output"),rubias=c("baseline","mixture","output")),wd=getwd())

```

###Create locus control and get genotype data
```{r locus control, echo=TRUE}

#CreateLocusControl.GCL(markersuite = "Chinook_NCI_39SNPs", username ="awbarclay", password = password)#Locus control

#LOKI2R.GCL(sillyvec="KEASTSC18",username="awbarclay",password)#Pull Data from LOKI

#save.image("V:/Analysis/2_Central/Chinook/Cook Inlet/2014/Mixture/ESSN_Chinook_2018_postseason/ESSN_Chinook_2018_postseason.Rdata")

load("V:/Analysis/2_Central/Chinook/Cook Inlet/2014/Mixture/ESSN_Chinook_2018_postseason/ESSN_Chinook_2018_postseason.Rdata")

```

###Create initial locus object
```{r initial locus object}

loci <- LocusControl$locusnames


```

##Data cleanup
###Check initial sample size
```{r initial sample size, echo=TRUE}

ColSize<-data.frame(row.names = "KEASTSC18")
ColSize$Original_N <- KEASTSC18.gcl$n
ColSize

```

###Removing individuals with <80% of loci with gentotypes
Fish that have gentoypes for less than 80% of loci are likely to have poor quality DNA and might introduce gentotyping errors into the mixture data and reduce the accruacy of the mixed stock analysis (MSA)
```{r missloci,echo=TRUE}

MissLOCI=RemoveIndMissLoci.GCL(sillyvec="KEASTSC18",proportion=0.8)
MissLOCI

ColSize$AfterMissLoci_N <- KEASTSC18.gcl$n
ColSize

```

###Check for duplicate individuals and remove them
Fish with 99% of scores that match
No duplicates to remove
```{r dupckeck, echo=TRUE, message=FALSE}

dupcheck<-CheckDupWithinSilly.GCL(sillyvec="KEASTSC18",loci=loci,quantile=NULL,minproportion=0.99)
dupcheck
```
```{r final sample size}
ColSize$Final_N <- KEASTSC18.gcl$n
ColSize

```

##Create BAYES baseline and get objects from baseline workspace
```{r get objects from baseline }

attach("V:/Analysis/2_Central/Chinook/Cook Inlet/2014/Baseline/CIChinook2014Baseline.RData")

groups<-ESSNGroups4

groupvec <- c(4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,1,1,1,2,1,2,1,1,1,2,2,3,4,4,4,4,4)

PooledNames54<-PooledNames54

basefortran<-CreateBaseline.GCL(sillyvec=PooledNames54,loci=loci,dir="BAYES/baseline",basename="CI54pops39loci",type="BAYES",groupvec=NULL)#BAYES
baseline<-create_rubias_baseline(sillyvec = PooledNames54,loci=loci,group_names = groups,groupvec = groupvec,baseline_name = "CI54pops39loci")#rubias

detach()
baseline
```

##Set up mixture objects
###Pool to mixture .gcl objects
```{r mixture setup}

attributes<-as.tibble(KEASTSC18.gcl$attributes)

mixtures<-attributes %>% 
  pull(CAPTURE_LOCATION) %>% 
  unique()

for(mix in mixtures){

  PoolCollections.GCL(collections="KEASTSC18",
                      loci=loci,
                      IDs=attributes %>% 
                        filter(CAPTURE_LOCATION==mix) %>% 
                        pull(FK_FISH_ID) %>%
                        as.character%>% 
                        list,
                      newname = mix
                      )
}

sapply(mixtures,function(mix){get(paste0(mix,".gcl"))$n})#Mixture sample sizes

```
###Create mixture inputs
####BAYES mixture files
```{r create BAYES mixture input files,echo=FALSE}

for(mix in mixtures){
  
  mixfortran<-CreateMixture.GCL(sillys = mix,loci=loci,mixname=mix,dir="BAYES/mixture")
  
}

```
####rubias mixture input files and object
```{r create rubias mixture input files,echo=FALSE}

mix.in<-create_rubias_mixture(sillyvec=mixtures,loci=loci,path = "rubias/mixture")
mix.in

```

##Create BAYES Control Files
###Priors and Initial starting values
Getting estimates from 2017 analysis to use as priors
```{r priors}

attach("V:/Analysis/2_Central/Chinook/Cook Inlet/2014/Mixture/2017 ESSN Chinook postseason analysis/ESSN2017PostseasonAnalysis.RData")

Kasilof_Early_prior<-TotalKasilofEarlyTable %>% as.tibble %>% pull(mean)

Kasilof_Late_prior<-TotalKasilofJulyTable %>% as.tibble %>% pull(mean)

Kenai_Late_prior<-TotalKenaiJulyTable %>% as.tibble %>% pull(mean)

detach()

```
###Dump control files
```{r bayes control files,echo=FALSE}

initmat<-MultiChainInits.GCL(npops=length(PooledNames54),nchains=5,prop=.9)

for(mix in mixtures){
  
  prior<-Prior.GCL(groupvec=groupvec,groupweights=get(paste0(mix,"_prior")),minval=0.01)

  CreateControlFile.GCL (sillyvec=PooledNames54,loci=loci,mixname=mix,basename="CI54pops39loci",suffix="",nreps=40000,nchains=5,groupvec=groupvec,priorvec=prior,initmat=initmat,dir="BAYES/control",seeds=matrix(sample(seq(10000),3*5),nrow=3),
                               thin=c(100,1,100),mixfortran=mixfortran,basefortran=basefortran,switches="F T F T T T F")
  
}

```
##Move BAYES file to output folder for analysis
```{r move BAYES files}
#Move files into output folders for running BAYES

 folders<-c("control","mixture")
 dir = paste0(getwd(),"/BAYES")
 
 bayesexe.paths=list.files("V:\\Analysis\\2_Central\\Chinook\\Cook Inlet\\2014\\Baseline\\BAYES\\BAYES exe files",full.names=T,include.dirs=T)
 
 bayesexe.files=list.files("V:\\Analysis\\2_Central\\Chinook\\Cook Inlet\\2014\\Baseline\\BAYES\\BAYES exe files",full.names=F,include.dirs=T)


#Move mixture and control files to output folder
 for(mix in mixtures){
   
   dir.create(path=paste0(dir,"/output/",mix))
 
    for(folder in folders){
          
          files=list.files(paste(dir,"/",folder,sep=''),pattern=mix) 
          
          paths=paste(dir,"/",folder,"/",files,sep='')
          
          for (path in paths){
            
            file.rename(from= path,to=sub(pattern=paste("BAYES/",folder,sep=''),x= path,replacement=paste("BAYES/output/",mix,sep=''),fixed=T))
                        
          }
    }
   
   file.copy(from=paste0(dir,"/baseline/CI54pops39loci.bse"),to=paste0(dir,"/output/",mix,"/CI54pops39loci.bse"))
   
   file.copy(from=bayesexe.paths,to=paste0("BAYES/output/",mix,"/",bayesexe.files))
   
 }  


```

